Two-Party State Channels with State Assertions

### 2019-01-14 paper/main.tex
Added email and updated contributions

	\institute{Kings College London, UK\\
		\email{patrick.mccorry@kcl.ac.uk}}

@@

\begin{itemize}
	\item We propose the first state channel that ensures an honest party never pays the cost to send the application's full state during the dispute process.
	\item This state channel is also the first to make the cost of progressing the application as part of a dispute process independent of the computational complexity of the application, and instead just a function of the number of transactions made in progressing the application.
	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 
\end{itemize}

>>>>

	\institute{Kings College London, UK\\
		\email{cpbuckland88@gmail.com}
		\email{patrick.mccorry@kcl.ac.uk}
	}

@@

\begin{itemize}
	\item We propose the first state channel that ensures an honest party never pays the cost to send the application's full state during the dispute process.
	\item Our state channel is also the first to ensure the cost of progressing an application is based only the number of transactions required to reach a terminal state, thus it is independent of the application's computational cost.
	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 
\end{itemize}
